An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-08 poly-embed-journal/poly-embed-journal.tex
Proving ish Lemma X

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\LV}{\mathcal{LV}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\OP}{\mathcal{OP}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

\jessie{Lemma X}
\begin{lemma}
	Let $\risk L: \simplex \to \reals$ be a (concave) polyhedral function.
	There exists a unique set of loss vectors $\LV$ of minimum cardinality such that $\risk L(p) = \min_{v \in \LV} \inprod{v}{p}$.
	Define $\Theta(v) = \{p \in \simplex \mid \inprod{v}{p} = \risk L(p)\}$.
	Furthermore, for all losses $L: \R \to \reals^\Y_+$ with Bayes risk $\risk L$, letting $\Gamma := \prop{L}$, there exists an $\R^* \subseteq \R$ such that
	\begin{enumerate}
		\item $\{L(r^*) \mid r^* \in \R^*\} = \LV$,
		\item $\R^*$ is a minimum representative set for $L$,
		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$,
		\item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
	\end{enumerate}
\end{lemma}
\begin{proof}
	Since $\risk L$ is a concave polyhedral function, it is the pointwise min of a finite set of linear functions \jessie{Rockafellar}.
	Since $\risk L$ is generated by a finite set of linear functions, the set of linear functions of minimum cardinality is well-defined.
	(1)
\end{proof}

>>>>

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\OP}{\mathcal{OP}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

\jessie{Lemma X}
\begin{lemma}
	Let $\risk L: \reals^n_+ \to \reals_+$ be a (concave) polyhedral function.
	There exists a unique set of loss vectors $\V$ of minimum cardinality such that $\risk L(p) = \min_{v \in \V} \inprod{v}{p}$.
	Define $\theta(v) = \{p \in \reals^n_+$\jessiet{$\simplex?$}$ \mid \inprod{v}{p} = \risk L(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
	Furthermore, for all losses $L: \R \to \reals^\Y_+$ with Bayes risk $\risk L : \reals^n_+ \to \reals_+$, letting $\Gamma := \prop{L}$, there exists an $\R^* \subseteq \R$ such that
	\begin{enumerate}
		\item $\{L(r^*) \mid r^* \in \R^*\} = \V$,
		\item $\R^*$ is a minimum representative set for $L$,
		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
		\item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
	\end{enumerate}
\end{lemma}
\newcommand{\epi}{\mathrm{epi}}
\begin{proof}
	Since $\risk L$ is a concave polyhedral function, it is the pointwise min of a finite set of linear functions by a corollary of~\citet[Theorem 19.1]{rockafellar1997convex}. %and therefore, the set of linear functions of minimum cardinality is well-defined and unique\jessiet{unique should be cite-able, but not sure where to find it.  My copy of Rockafellar is in COS right now.}.
	By the same result, we know that $E_L := \epi(\risk L)$ is closed and has finitely many faces.
	Form $\V$ by iterating over $E_L$'s finitely many faces as follows:
	for each face $F$, we know there is a vector $v$ generating the face \jessiet{That is, $p \mapsto (p, \inprod{p}{v})$ supports $\risk L$ on [exactly] face $F$.}. 
	If there is a point $p_v \in F$ such that $\risk L$ is differentiable at $p_v$,\jessiet{Is this the condition we want? Dancing around facets} add $v$ to $\V$.

	\jessiet{Differentiable implies subgradient is single-valued implies supporting hyperplane is unique, right?}
	$\V$ is then unique since $\partial \risk L(p_v) = \{\partial \inprod{p_v}{v}\}$ \jessiet{is this right?} for each $p_v$, and therefore the hyperplane $p \mapsto (p, \inprod{p}{v})$ uniquely supports $\risk L$ at $p_v$.
	Moreover, since $\V$ is finite and for each $v \in \V$ there is a $p_v$ such that $\partial \risk L(p_v)$ is single-valued, no $v$ can be removed from $\V$, so it has the smallest cardinality possible. \jessiet{Explicitly: using integer cardinality here.}

	Now suppose there is a loss $L:\R \to \reals_+^\Y$ with Bayes risk $\risk L : p \mapsto \min_{r \in \R} \inprod{p}{L(r)}$.
	Construct $\R^*$ by iterating over $\V$; for each $v \in \V$, there must be some $r^* \in \R$ such that $L(r^*) = v$ since $\V$ is unique.
	(Therefore, there is some $p_v$ such that $p \mapsto (p, \inprod{p}{v})$ uniquely supports $\risk L$ at $p_v$, so we must have $L(r^*) = v$.)

	(1) and (2) follow immediately.
	(3) and (4) follow since $\Gamma_r$ can be re-written as $\{p \in \reals_+^n$\jessiet{$\simplex?$}$ \mid \inprod{p}{L(r)} = \risk L(p)\}$.

	Since $E_L$ is a convex polyhedron in $\reals^{n+1}_+$\jessiet{nonnegative okay? looking at Aurenhammer's paper, I only see results on $\reals^n$.}, we can take a linear projection of the faces of $E_L$ onto $\reals^n_+$ \jessie{nonnegative?} to yield an affinely equivalent cell complex $C$ (Definition~\ref{def:cell-complex}), which is a power diagram by Theorem~\ref{thm:aurenhammer}.
	Thus, every level set of $\Gamma$ is a cell in the induced power diagram.
	Since, for each $r \in \R^*$, there is a $p_r$ such that $\Gamma(p_r) = \{r\}$\jessiet{need to justify (using fact about infections from subgradient to property values?)}, we must have $\Gamma_{r}$ not a subset of any other level set, and therefore must be full-dimensional relative to $\reals^{n}$.\jessiet{??}
	Moreover, if there was a full-dimensional level set $\Gamma_{r'}$ such that $\Gamma_{r'} \not \in \Theta$, then \jessie{contradict representative}.
	(4) follows since any cell of a power diagram is contained in some $n-1$-dimensional face $F$, and there must be some $r^* \in \R^*$ such that $\Gamma_{r^*} = F$.
